Methods and Results

### 2022-05-02 ms.Rmd
Coding in version numbers so it's autoupdated, remove autochache and ggsave all figures. Small spelling mistakes corrected.

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: false
      reference_docx: template.docx
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

@@

  # Now reparameterize model
  model1.5_2 <- rma.mv(SMDH ~ 0 + Harm_type + zSSD, V = data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), test = "t", data = data)

     robust_model1.5_2 <- robust(model1.5_2, cluster = data$study, vcov = "CR2")
  robust_model1.5_2_PI <- pred_interval(model1.5_2, c(5.1796, -0.6908, 3.0189, 1.9679))

@@

#### Meta-analysis
We analysed effect size data using the *metafor* @Metafor (vers 2.4.0) package in R @R (vers 4.0.5). To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological. We plotted overall meta-analytic means using the orchard plot package @NakaOrchard. Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study. To control for sources of non-independence, we included study and species-level random effects @Noble2017. We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl. We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers 5.4.1). Overall, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`). As such, we did not include phylogeny in our models.

@@

Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`). This strong effect held even when accounting for within-study non-independence (Meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`). However, visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)). Evidence for publication bias was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`), and this held true when accounting for heterogenity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`). Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguisable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`). These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published.

When accounting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects. The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).

@@

harm_plot <- ggplot(data, aes(x = Harm_type, y = SMDH)) + 
              geom_violin(alpha = 0.2, aes(fill = Harm_type, colour = Harm_type)) + 
              #geom_point() + don't need this because we have geom_jitter. It will otherwise double plot points
              ylim(c(-2, 6.5)) + 
              geom_jitter(aes(x = Harm_type, y = SMDH, fill = Harm_type, colour = Harm_type, size = 1/sqrt(v_SMDH)),
                          width = 0.08, alpha = 0.2) + 
              theme_bw() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Harm Type", 
                   y = "SMDH", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
              scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 3, 1)), y = 6.45, 
                       label= paste0("italic(n)==", robust_model1.5_2_PI$n), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 3, 1)), y = 6.15, 
                       label= paste0("italic(k)==", robust_model1.5_2_PI$nstudy), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = robust_model1.5_2_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
        	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = robust_model1.5_2_PI, aes(x = moderator, y = Est, colour= moderator), size = 5)+
              geom_segment(aes(x = 1, y = 4.8, xend = 2, yend = 4.8), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
              geom_segment(aes(x = 1, y = 5.5, xend = 3, yend = 5.5), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 4) + 
              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 4) 
              #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)

harm_plot
```

@@

p3
```

@@

Species with higher sperm intensity exhibited a significant reduction in female fitness with higher male harm (overall meta-analytic mean: `r robust_model1.7_reparam$beta[1]`, 95% CI: `r robust_model1.7_reparam$ci.lb[1]` to `r robust_model1.7_reparam$ci.ub[1]`, p = `r p_value(robust_model1.7_reparam$pval[1])`), wheras the same was not true of species with low sperm intensity (overall meta-analytic mean: `r robust_model1.7_reparam$beta[2]`, 95% CI: `r robust_model1.7_reparam$ci.lb[2]` to `r robust_model1.7_reparam$ci.ub[2]`, p = `r p_value(robust_model1.7_reparam$pval[2])`) (Figure \@ref(fig:sperm)). Overall, there was no significant difference between species deemed to have high sperm intensity compared to those with low sperm intensity (Figure \@ref(fig:sperm)).

@@

sperm_plot

>>>>

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: false
      reference_docx: template.docx
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

@@

  # Now reparameterize model
  model1.5_2 <- rma.mv(SMDH ~ 0 + Harm_type + zSSD, V = data$v_SMDH, 
                     random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", data = data)

     robust_model1.5_2 <- robust(model1.5_2, cluster = data$study)

  robust_model1.5_2_PI <- pred_interval(model1.5_2, c(5.1796, -0.6908, 3.0189, 1.9679))

@@

#### Meta-analysis
We analysed effect size data using the *metafor* @Metafor (vers `utils::packageVersion("metafor")`) package in R @R (vers `r paste0(R.Version()$major, ".", R.Version()$minor)`). To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological. We plotted overall meta-analytic means using the orchard plot package @NakaOrchard. Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study. To control for sources of non-independence, we included study and species-level random effects @Noble2017. We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl (vers `r utils::packageVersion("rotl")`. We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers `r utils::packageVersion("ape")`). Overall, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`). As such, we did not include phylogeny in our models.

@@

Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`). This strong effect held even when accounting for within-study non-independence (Meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`). Visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)), which was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`). This result held true when accounting for heterogeneity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`). Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguishable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`). These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published, however, it is important to recognise that we cannot know for sure what (if anything) is generating such a bias.

When accounting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects. The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`)(Table \@ref(tab:pretty_table).

@@

harm_plot <- ggplot(data, aes(x = Harm_type, y = SMDH)) + 
              geom_violin(alpha = 0.2, aes(fill = Harm_type, colour = Harm_type)) + 
              #geom_point() + don't need this because we have geom_jitter. It will otherwise double plot points
              ylim(c(-2, 6.5)) + 
              geom_jitter(aes(x = Harm_type, y = SMDH, fill = Harm_type, colour = Harm_type, size = 1/sqrt(v_SMDH)),
                          width = 0.08, alpha = 0.2) + 
              theme_bw() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Harm Type", 
                   y = "SMDH", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
              scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 3, 1)), y = 6.45, 
                       label= paste0("italic(n)==", robust_model1.5_2_PI$n), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 3, 1)), y = 6.15, 
                       label= paste0("italic(k)==", robust_model1.5_2_PI$nstudy), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = robust_model1.5_2_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
        	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = robust_model1.5_2_PI, aes(x = moderator, y = Est, colour= moderator), size = 5)+
              geom_segment(aes(x = 1, y = 4.8, xend = 2, yend = 4.8), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
              geom_segment(aes(x = 1, y = 5.5, xend = 3, yend = 5.5), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 4) + 
              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 4) 
              #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)
ggsave(plot = harm_plot, filename = "fig2.png", path = "./output/figs", height = 7.416667, width = 13.805556, device = "png", dpi = 600)
harm_plot
```

@@

ggsave(plot = p3, filename = "fig3.png", path = "./output/figs", height = 7, width = 10, device = "png", dpi = 600)
p3
```

@@

Species with higher sperm intensity exhibited a significant reduction in female fitness with higher male harm (overall meta-analytic mean: `r robust_model1.7_reparam$beta[1]`, 95% CI: `r robust_model1.7_reparam$ci.lb[1]` to `r robust_model1.7_reparam$ci.ub[1]`, p = `r p_value(robust_model1.7_reparam$pval[1])`), whereas the same was not true of species with low sperm intensity (overall meta-analytic mean: `r robust_model1.7_reparam$beta[2]`, 95% CI: `r robust_model1.7_reparam$ci.lb[2]` to `r robust_model1.7_reparam$ci.ub[2]`, p = `r p_value(robust_model1.7_reparam$pval[2])`) (Figure \@ref(fig:sperm)). Overall, there was no significant difference between species deemed to have high sperm intensity compared to those with low sperm intensity (Figure \@ref(fig:sperm)).

@@

ggsave(plot = sperm_plot, filename = "fig4.png", path = "./output/figs", height = 7, width = 10, device = "png", dpi = 600)
sperm_plot
